Conditional selectivity for Hexastores

### 2011-07-20 conditional/trunk/selectivity-hexastore.tex
Add variables to selectivity
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@22 43ef1190-90fd-4dd7-a769-d0121f02b80e
add todo section
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@23 43ef1190-90fd-4dd7-a769-d0121f02b80e
Add example to hexastore section
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@24 43ef1190-90fd-4dd7-a769-d0121f02b80e

\subsection{Example}

@@

Now, given a query, we shall explain how the selectivity can be
computed exactly rather than being estimated. First, we define a
function $cm(x)$ which returns the number of matches of a given SPARQL
term $x$. \todo{needs to be a lot more precise}

Then, 
\begin{equation}
sel(S) = \frac{cm(s_i)}{i} ,
\end{equation}
\begin{equation}
sel(P|S) = \frac{cm(p_{n_i}^i)}{n_i}
\end{equation}
and
\begin{equation}
sel(O|S \cap P) = \frac{cm(o_{k_{i,n_i}}^{i,n_i})}{k_{i,n_i}}
\end{equation}

>>>>

\subsection{Example}\label{sec:example}

@@

Let us return to the example in section~\ref{sec:example}: We have
$s_1 = \texttt{key-for-alice}$ and $i=2$. Further, $p_1^1 =
\texttt{key-for-foaf:firstName}$, $p_2^1 = \texttt{key-for-rdf:type}$ and $p_3^1 =
\texttt{key-for-rel:spouseOf}$ and $n_1 = 3$. For each predicate, there is only
one object, so $k_{1,1} = 1$ and $o_{1_{1,1_1}}^{1,1_1} = \texttt{key-for-Alice-literal}$.

Now, given a query, we shall explain how the selectivity can be
computed exactly rather than being estimated. First, we define a
function $cm(x)$ which returns the number of matches of a given key
$x$\todo{argue the term-key-connection}. \todo{needs to be a lot more precise}

Then, 
\begin{equation}
sel(S = s_i) = \frac{cm(s_i)}{i} ,
\end{equation}
\begin{equation}
sel(P = p_{n_i}^i|S = s_i) = \frac{cm(p_{n_i}^i)}{n_i}
\end{equation}
and
\begin{equation}
sel(O = o_{k_{i,n_i}}^{i,n_i} |S = s_i \cap P = p_{n_i}^i) =
\frac{cm(o_{k_{i,n_i}}^{i,n_i})}{k_{i,n_i}} .
\end{equation}

\section{Further work on conditional selectivity}

\todo{this section}
